Template report example

### 2023-10-12 dev/dev_template_report.Rmd
streamFindData not StreamFindData

# Libraries
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(streamFind)

@@

# Add logo file
path_extdata <- system.file(package = "streamFindData", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png") #207 x 216 px
```

>>>>

# Libraries
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(StreamFind)

@@

# Add logo file
path_extdata <- system.file(package = "StreamFindData", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png") #207 x 216 px
```
